A Comparative study of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-22 latex/paper.tex
Updated figures and started working on histogram section

%%% HISTOGRAM %%%
\subsection{Histogram: Number of workers}

@@

\subsection{Histogram: Number of blocks}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bids_worker.png}%
        \caption{Histogram makespan}\label{fig:bids_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bids_idle_worker.png}%
        \caption{Histogram total time}\label{fig:bids_tt_worker}
    \end{subfigure}
    \caption{Variation of the amount of worker, 8 threads/worker}
\end{figure}

@@

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_bids_gantt.png}
        \caption{Spark}\label{fig:bids_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bag_bids_gantt.png}%
        \caption{Dask Bag}\label{fig:bids_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/delayed_bids_gantt.png}%
        \caption{Dask Delayed}\label{fig:bids_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/futures_bids_gantt.png}%
        \caption{Dask Futures}\label{fig:bids_dask_futures_gantt}
    \end{subfigure}
    \caption{Gantt chart with 8 workers}\label{fig:bids_gantt}
\end{figure*}

>>>>

%%% HISTOGRAM %%%
\subsection{Histogram: Number of workers}
Figure~\ref{fig:histo_ms_worker} shows the makespan of the application for various
amounts of workers. Spark is tremendiously faster than Dask APIs. The difference
narrows as the number of workers increases. Between Dask APIs there is no substantial
difference, however, Bag is slightly faster on average.

From Figure~\ref{fig:histo_tt_worker} the total time spend in each function is shown.
The computation time is significantly larger in Dask than Spark. This is potentially
due to Python's GIL preventing Dask to parallelize the computation on multiple thread.
Overall, the IO and overhead is comparable for all engines.

@@

\subsection{Histogram: Number of blocks}
Figure~\ref{fig:histo_ms_block}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bids_worker.png}%
        \caption{BIDS App example makespan}\label{fig:bids_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bids_idle_worker.png}%
        \caption{BIDS App example total time}\label{fig:bids_tt_worker}
    \end{subfigure}
    \caption{Variation of the amount of worker, 8 threads/worker}
\end{figure}

@@

% \begin{figure*}[!htb]
%     \centering
%     \begin{subfigure}[b]{\columnwidth}
%         \includegraphics[clip,width=\columnwidth]{images/spark_bids_gantt.png}
%         \caption{Spark}\label{fig:bids_spark_gantt}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[b]{\columnwidth}
%         \includegraphics[clip,width=\columnwidth]{images/bag_bids_gantt.png}%
%         \caption{Dask Bag}\label{fig:bids_dask_bag_gantt}
%     \end{subfigure}
%     \\
%     \begin{subfigure}[b]{\columnwidth}
%         \includegraphics[clip,width=\columnwidth]{images/delayed_bids_gantt.png}%
%         \caption{Dask Delayed}\label{fig:bids_dask_delayed_gantt}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[b]{\columnwidth}
%         \includegraphics[clip,width=\columnwidth]{images/futures_bids_gantt.png}%
%         \caption{Dask Futures}\label{fig:bids_dask_futures_gantt}
%     \end{subfigure}
%     \caption{Gantt chart with 8 workers}\label{fig:bids_gantt}
% \end{figure*}
